Stream of Consciousness Literature: A 'Joyceless' Linguistic Landscape

### 2024-04-05 paper/paper.qmd
paper update
update introduction

Thus, my estimand is the correlation between mental health-related words in SOC literature, their frequency and sentiment value as provided by @sentiment. This is considered in terms of nine selected SOC novels only, namely Joyce's \textit{A Portrait of the Artist as a Young Man and Chamber Music}; Woolf's \textit{Mrs Dalloway and Jacob's Room}; Proust's \textit{Swann Way}; Mansfield's \textit{Bliss and The Garden Party}; and Eliot's \textit{The Waste Land and The Love Song of J. Alfred Prufrock}. Through our analysis, we found that (percentage, number and data here, main results)...

@@

>>>>

Thus, my estimand is the correlation between mental health-related words in SOC literature, their frequency and sentiment value as provided by @Tidytext. This is considered in terms of nine selected SOC novels only, namely Joyce's \textit{A Portrait of the Artist as a Young Man and Chamber Music}; Woolf's \textit{Mrs Dalloway and Jacob's Room}; Proust's \textit{Swann Way}; Mansfield's \textit{Bliss and The Garden Party}; and Eliot's \textit{The Waste Land and The Love Song of J. Alfred Prufrock}. Through our analysis, we found that (percentage, number and data here, main results)...

@@

## Data Limitations
